---
title: "03-house_prices_exp"
author: "Christian Urcuqui"
date: "21 de marzo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exploration with R

## Libraries 


```{r lib, include=FALSE, warning=FALSE, message=FALSE}
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("pastecs")
#install.packages("psych")
#install.packages("psych")
#install.packages("ggcorrplot")
#install.packages("fastDummies")

library(ggplot2)
library(dplyr)
library(pastecs)
library(psych)
library(ggcorrplot)
library(fastDummies)
```


## Load the datasets

```{r data, include=FALSE}
train <-read.csv("D:/Usuarios/rhaps/OneDrive/Clases/2019-1/Analisis exploratorio/clase2/train.csv", stringsAsFactors=FALSE)
```


## Understand the Problem

```{r us1, include=FALSE, warning=FALSE, message=FALSE}
str(train)
```

### Data Transformation and Cleaning

Let's use the next script which has some activities for transforming and cleaning 

```{r clearning, include=FALSE, warning=FALSE, message=FALSE}
source("03-limpiar_transformar.R")
train_clean <- lt_house(train)
```

## Univariable Study

### Analysing 'SalePrice'


```{r us2, include=FALSE, warning=FALSE, message=FALSE}
summary(train_clean$saleprice)
```

De este podemos inferir que nuestro precio minimo por lo menos es más grande que cero. Ahora veamos como esta la distribución de estos datos.


```{r us3, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_histogram(mapping = aes(train_clean$saleprice, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("precio de venta")
```
  
  
+ Podemos concluir que no tiene una distribución normal
+ Tiene una asimetría positiva 
+ Tiene un pico 


```{r us4, include=FALSE, warning=FALSE, message=FALSE}

describe(train_clean$saleprice)

```

Slide 41

```{r us5, include=FALSE, warning=FALSE, message=FALSE}

boxplot(train_clean$saleprice, main="SalePrice")

```

Slide 42

```{r us5, include=FALSE, warning=FALSE, message=FALSE}
source("outliers_script.R")
outlierKD(train_clean,saleprice)
```

Slide 43
```{r us5, include=FALSE, warning=FALSE, message=FALSE}
qnt <- quantile(train_clean$saleprice, probs=c(.25, .75), na.rm = T)

H <- 1.5 * IQR(train_clean$saleprice, na.rm = T)

atipicosraz<-ifelse(train_clean$saleprice > qnt[2]+H | train_clean$saleprice < qnt[1]-H ,1,0)

ggplot(train_clean) + 
  geom_boxplot(mapping=aes(x="", y=saleprice)) +
  geom_hline(yintercept=qnt, color="red") + 
  geom_hline(yintercept=qnt[2]+H, color="blue") +
  geom_hline(yintercept=qnt[1]-H, color="blue") 

```


## Multivariate Study

Let's analyze the relationthip between the features:

+ GrLivArea, Above grade (ground) living area square feet.
+ TotalBsmtSF, Total square feet of basement area.
+ LotArea: Lot size in square feet

```{r mul1, include=FALSE, warning=FALSE, message=FALSE}

# primer plot

ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$grlivarea, y=train_clean$saleprice)) + 
  xlab("grlivarea") + 
  ylab("saleprice")

# segundo plot

ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$totalbsmtsf, y=train_clean$saleprice)) + 
  xlab("totalbsmtsf") + 
  ylab("saleprice")

# segundo plot con linea

plot(train_clean$totalbsmtsf, train_clean$saleprice,
     xlab = "totalbsmtsf", ylab = "saleprice",
     pch = 19, frame = FALSE)
abline(lm(saleprice ~ totalbsmtsf, data = train_clean), col = "blue")

# tercer plot con exponencial
ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$totalbsmtsf, y=train_clean$saleprice)) + 
  geom_smooth(mapping = aes(x=train_clean$totalbsmtsf, y=train_clean$saleprice)) + 
  xlab("totalbsmtsf") + 
  ylab("saleprice")

```


## Relationship with categorical features

```{r mul2, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_boxplot(mapping = aes(x=train_clean$overallqual, y=train_clean$saleprice, fill=train_clean$overallqual)) + 
  xlab("overallqual") + 
  ylab("saleprice")
```

```{r mul3, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_boxplot(mapping = aes(x=factor(train_clean$yearbuilt), y=train_clean$saleprice, fill=train_clean$yearbuilt)) +
  xlab("yearbuilt") + 
  ylab("saleprice")
```

## objective analysis

slides 29-30
```{r ob1, include=FALSE, warning=FALSE, message=FALSE}

corr <- round(cor(dplyr::select_if(train_clean, is.numeric)), 1)

head(corr[, 1:6])

ggcorrplot(corr, hc.order = TRUE, type = "lower",
   lab = TRUE)

sort(corr[,'saleprice'] )

```


slide 49
```{r ob2, include=FALSE, warning=FALSE, message=FALSE}
columns_interested <- c('saleprice', 'grlivarea', 'garagecars', 'totalbsmtsf', 'fullbath')
pairs(train_clean[,columns_interested])
```


slide 64
```{r ob3, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$grlivarea, y=train_clean$saleprice)) + 
  xlab("grlivarea") + 
  ylab("saleprice") 

# slide 65-67

ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$grlivarea, y=train_clean$saleprice, color=train_clean$overallqual)) + 
  xlab("grlivarea") + 
  ylab("saleprice") 

train_clean[train_clean$grlivarea >= 4500, ]


ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$grlivarea, y=train_clean$saleprice, color=train_clean$landcontour)) + 
  xlab("grlivarea") + 
  ylab("saleprice") 

train_clean <- train_clean[train_clean$grlivarea < 4500, ]


```

probplot - probability plot
Generates a probability plot for a specified theoretical distribution, i.e., basically a qqplot where the y-axis is labeled with probabilities instead of quantiles. The function is mainly intended for teaching the concept of quantile plots.

```{r prob1, include=FALSE, warning=FALSE, message=FALSE}
qqnorm(train_clean$saleprice)
qqline(train_clean$saleprice)
```


slide 71
```{r prob2, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_histogram(mapping = aes(log(train_clean$saleprice), alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("precio de venta - transformación")

qqnorm(log(train_clean$saleprice))
qqline(log(train_clean$saleprice))

train_clean$saleprice_log <- log(train_clean$saleprice)

```

slide 72
```{r prob3, include=FALSE, warning=FALSE, message=FALSE}


ggplot(train_clean) + 
  geom_histogram(mapping = aes(train_clean$grlivarea, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("grlivarea")

ggplot(train_clean) + 
  geom_histogram(mapping = aes(train_clean$totalbsmtsf, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("totalbsmtsf")


ggplot(train_clean) + 
  geom_histogram(mapping = aes(log(train_clean$grlivarea), alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("grlivarea")



qqnorm(log(train_clean$grlivarea))
qqline(log(train_clean$grlivarea))

train_clean$grlivarea_log <- log(train_clean$grlivarea)

ggplot(train_clean) + 
  geom_histogram(mapping = aes(train_clean$totalbsmtsf, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("totalbsmtsf")

# error ocasionado
#qqnorm(log(train_clean$totalbsmtsf))
#qqline(log(train_clean$totalbsmtsf))

# slide 74

# how many totalbsmts==0 the dataset has?
prop.table(table(ifelse(train_clean$totalbsmtsf>0, TRUE, FALSE)))

# let's analyze the data without 0
segmented <- train_clean[train_clean$totalbsmtsf>0,]$totalbsmtsf

ggplot() + 
  geom_density(mapping = aes(log(segmented), alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("totalbsmtsf")
qqnorm(log(segmented))
qqline(log(segmented))

segmented <- log(segmented)

```

slide 75
```{r prob4, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean[train_clean$totalbsmtsf>0,]) + 
  geom_point(mapping = aes(x=grlivarea_log, y=saleprice_log)) + 
  xlab("grlivarea") + 
  ylab("saleprice") 

```
slide 75
```{r prob4, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean[train_clean$totalbsmtsf>0,]) + 
  geom_point(mapping = aes(x=segmented, y=saleprice_log)) + 
  xlab("totalbsmtsf") + 
  ylab("saleprice") 

```

slide 78
```{r dumm, include=FALSE, warning=FALSE, message=FALSE}
# dummy
dummy_variables <- fastDummies::dummy_cols(train_clean$street)
#names(dummy_variables)[1] <- "street"
colnames(dummy_variables) <- c("street", "streetpave", "streetgrvl")
# merge
new_dataset <- merge(train_clean[,c('street','lotfrontage','utilities')],dummy_variables, by="street") 
new_dataset
```


## new exploration

### make new variables


slide 78
```{r exploreadd, include=FALSE, warning=FALSE, message=FALSE}
# we can make another variable which includes the total area

train_clean$totalsf <- train_clean$totalbsmtsf + train_clean$x1stflrsf + train_clean$x2ndflrsf
ggplot(train_clean) + 
  geom_histogram(mapping = aes(totalsf, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("totalsf")

ggplot(train_clean) + 
  geom_density(mapping = aes(log(totalsf), alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("totalsf")

qqnorm(log(train_clean$totalsf))
qqline(log(train_clean$totalsf))

train_clean$totalsflog <- log(train_clean$totalsf) 

ggplot(train_clean) + 
  geom_point(mapping = aes(x=totalsflog, y=saleprice_log)) + 
  xlab("totalsf") + 
  ylab("saleprice") 

```

```{r exploreadd, include=FALSE, warning=FALSE, message=FALSE}
dummy_variables <- fastDummies::dummy_cols(train_clean$overallqual)
#names(dummy_variables)[1] <- "overallqual"
colnames(dummy_variables) <- c("overallqual", "ovqgood", "ovqaboveaverage", "ovqverygood", "ovqaverage", "ovqexcellent", "ovqbelowaverage", "ovqveryexcellent", "ovqfair", "ovqpoor")
# merge

new_dataset <- merge(train_clean[,c('overallqual','totalsflog','grlivarea_log', "saleprice_log")],dummy_variables, by="overallqual") 
summary(new_dataset)
```

### training phase


```{r traning, include=FALSE, warning=FALSE, message=FALSE}
modelo_mpl<-lm(saleprice_log~ grlivarea_log+totalsflog+ovqgood+ovqaboveaverage+ovqverygood+ovqaverage+ovqexcellent+ovqbelowaverage+ovqveryexcellent+ovqfair,  data=new_dataset)
summary(modelo_mpl)

```

### testing phase

```{r testing, include=FALSE, warning=FALSE, message=FALSE}
test <-read.csv("D:/Usuarios/rhaps/OneDrive/Clases/2019-1/Analisis exploratorio/clase2/test.csv", stringsAsFactors=FALSE) 
colnames(test)<- tolower(colnames(test))
test$totalsf <- test$totalbsmtsf + test$x1stflrsf + test$x2ndflrsf
test <- test[,c("id","grlivarea", "street", "totalsf", "overallqual")]
test$grlivarea_log <- log(test$grlivarea)
test$totalsflog <- log(test$totalsf)

dummy_variables_test <- fastDummies::dummy_cols(test$overallqual)
colnames(dummy_variables_test) <- c("overallqual", "ovqaverage", "ovqaboveaverage", "ovqverygood", "ovqgood", "ovqbelowaverage", "ovqexcellent", "ovqpoor", "ovqfair", "ovqveryexcellent", "ovqverypoor")
# merge
new_dataset_test <- cbind(test[,c('overallqual','totalsflog','grlivarea_log')], dummy_variables_test[,2:11])

saleprice_pred <- predict(object=modelo_mpl,new_dataset_test[,c("grlivarea_log", "totalsflog", "ovqgood", "ovqaboveaverage", "ovqverygood", "ovqaverage", "ovqexcellent", "ovqbelowaverage", "ovqveryexcellent", "ovqfair")]) 

test$prediction <- exp(saleprice_pred)

names(test)[1]<-"Id"
names(test)[8]<-"SalePrice"

write.csv2(test[,c(1,8)], "test_1_housep.csv")

```