---
title: "03-house_prices_exp"
author: "Christian Urcuqui"
date: "21 de marzo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exploration with R

## Load the datasets

```{r data, include=FALSE}
train <-read.csv("D:/Usuarios/rhaps/OneDrive/Clases/2019-1/Analisis exploratorio/clase2/train.csv", stringsAsFactors=FALSE)
test <-read.csv(file.choose(), stringsAsFactors=FALSE) 
```

## Libraries 


```{r lib, include=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(pastecs)
```

## Understand the Problem

```{r us1, include=FALSE, warning=FALSE, message=FALSE}
str(train)
```

### Data Transformation and Cleaning

Let's use the next script which has some activities for transforming and cleaning 

```{r clearning, include=FALSE, warning=FALSE, message=FALSE}
source("03-limpiar_transformar.R")
train_clean <- lt_house(train)
```

## Univariable Study

### Analysing 'SalePrice'


```{r us2, include=FALSE, warning=FALSE, message=FALSE}
summary(train_clean$saleprice)
```



De este podemos inferir que nuestro precio minimo por lo menos es más grande que cero. Ahora veamos como esta la distribución de estos datos.


```{r us3, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_histogram(mapping = aes(train_clean$saleprice, alpha= 2, fill="red")) +
  scale_x_continuous() +
  theme(legend.position="none") + 
  xlab("precio de venta")
```
  
  
+ Podemos concluir que no tiene una distribución normal
+ Tiene una asimetría positiva 
+ Tiene un pico 


```{r us4, include=FALSE, warning=FALSE, message=FALSE}


library(psych)
describe(train_clean$saleprice)


```


## Multivariate Study

Let's analyze the relationthip between the features:

+ GrLivArea, Above grade (ground) living area square feet.
+ TotalBsmtSF, Total square feet of basement area.
+ LotArea: Lot size in square feet

```{r mul1, include=FALSE, warning=FALSE, message=FALSE}
ggplot(train_clean) + 
  geom_point(mapping = aes(x=train_clean$grlivarea, y=train_clean$saleprice)) + 
  xlab("grlivarea") + 
  ylab("saleprice")
```

## Test Assumptions
